Reference Tracking Strategies of Native and Late Signers in Turkish Sign Language

### 2023-01-28 revised_manuscript.Rmd
update
Removed participant 13 and updated labels for the plots.

# statistics libraries
library(brms) # bayesian modeling
library(bayesplot) # plot options for bayesian models
bayesplot_theme_set(new = theme_bw()) # set plot theme
library(tidybayes)
library(bayestestR)
theme_apa <- function(base_size = 10, base_family = "serif", box = FALSE) {
  adapted_theme <- ggplot2::theme_bw(base_size, base_family) +
    ggplot2::theme(legend.position = "bottom",
                   plot.title = ggplot2::element_text(size = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, ggplot2::rel(14), 0))
                   # , axis.title = ggplot2::element_text(size = ggplot2::rel(1.1))
                   , axis.title.x = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(ggplot2::rel(12), 0, 0, 0))
                   , axis.title.y = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, ggplot2::rel(12), 0, 0))
                   , axis.title.y.right = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(12)))
                   , axis.ticks.length = ggplot2::unit(ggplot2::rel(6), "points")
                   , axis.text = ggplot2::element_text(size = ggplot2::rel(0.9))
                   , axis.text.x = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(ggplot2::rel(6), 0, 0, 0))
                   , axis.text.y = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(0, ggplot2::rel(6), 0, 0))
                   , axis.text.y.right = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(6)))
                   , axis.line = ggplot2::element_line()
                   # , axis.line.x = ggplot2::element_line()
                   # , axis.line.y = ggplot2::element_line()
                   , legend.title = ggplot2::element_text()
                   , legend.key = ggplot2::element_rect(fill = NA, color = NA)
                   , legend.key.width = ggplot2::unit(ggplot2::rel(20), "points")
                   , legend.key.height = ggplot2::unit(ggplot2::rel(20), "points")
                   , legend.margin = ggplot2::margin(
                     t = ggplot2::rel(16)
                     , r = ggplot2::rel(16)
                     , b = ggplot2::rel(16)
                     , l = ggplot2::rel(16)
                     , unit = "points"
                   )
                   , panel.spacing = ggplot2::unit(ggplot2::rel(14), "points")
                   , panel.grid.major.x = ggplot2::element_blank()
                   , panel.grid.minor.x = ggplot2::element_blank()
                   , panel.grid.major.y = ggplot2::element_blank()
                   , panel.grid.minor.y = ggplot2::element_blank()
                   , strip.background = ggplot2::element_rect(fill = NA, color = NA)
                   , strip.text.x = ggplot2::element_text(size = ggplot2::rel(1.2), margin = ggplot2::margin(0, 0, ggplot2::rel(10), 0))
                   , strip.text.y = ggplot2::element_text(size = ggplot2::rel(1.2), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(10)))
    )
  if(box) {
    adapted_theme <- adapted_theme + ggplot2::theme(panel.border = ggplot2::element_rect(color = "black"))
  } else {
    adapted_theme <- adapted_theme + ggplot2::theme(panel.border = ggplot2::element_blank())
  }
  adapted_theme
}

@@

@@

# Posterior plot for reference type
df_model_1 <- mcmc_intervals_data(model_1, pars = vars(starts_with("b_")))
df_model_1$parameter %<>% dplyr::recode(`b_muNominal_Intercept` = "Nom_Intercept",
                                        `b_muNull_Intercept` = "Null_Intercept",
                                        `b_muNominal_Nativeness1` = "Nom_Native",
                                        `b_muNull_Nativeness1` = "Null_Native",
                                        `b_muNominal_Discourse1` = "Nom_Intro",
                                        `b_muNominal_Discourse2` = "Nom_Maintain",
                                        'b_muNominal_Nativeness1:Discourse1' = 'Nom_Native*Intro',
                                        'b_muNominal_Nativeness1:Discourse2' = 'Nom_Native*Maintain',
                                        'b_muNull_Nativeness1:Discourse1' = 'Null_Native*Intro',
                                        'b_muNull_Nativeness1:Discourse2' = 'Null_Native*Maintain',
                                        `b_muNull_Discourse1` = "Null_Intro",
                                        `b_muNull_Discourse2` = "Null_Maintain")
saveRDS(df_model_1, "./rds/df_model_1.rds")

@@

# Posterior plot for reference type
df_model_3 <- mcmc_intervals_data(model_3, pars = vars(starts_with("b_")))
df_model_3$parameter %<>% dplyr::recode(`b_muNominal_Intercept` = "Nom_Intercept",
                                        `b_muNull_Intercept` = "Null_Intercept",
                                        `b_muNominal_Group2M1` = "Nom_Late1-Late2",
                                        `b_muNominal_Group3M2` = "Nom_Native-Late1",
                                        `b_muNominal_Discourse1` = "Nom_Intro",
                                        `b_muNominal_Discourse2` = "Nom_Maintain",
                                        `b_muNominal_Group2M1:Discourse1` = 'Nom_L1-L2*Intro',
                                        `b_muNominal_Group3M2:Discourse1` = 'Nom_N-L1*Intro',
                                        `b_muNominal_Group2M1:Discourse2` = 'Nom_L1-L2*Maintain',
                                        `b_muNominal_Group3M2:Discourse2` = 'Nom_N-L1*Maintain',
                                        `b_muNull_Group2M1` = "Null_Late1-Late2",
                                        `b_muNull_Group3M2` = "Null_Native-Late1",
                                        `b_muNull_Discourse1` = "Null_Intro",
                                        `b_muNull_Discourse2` = "Null_Maintain",
                                        `b_muNull_Group2M1:Discourse1` = 'Null_L1-L2*Intro',
                                        `b_muNull_Group3M2:Discourse1` = 'Null_N-L1*Intro',
                                        `b_muNull_Group2M1:Discourse2` = 'Null_L1-L2*Maintain',
                                        `b_muNull_Group3M2:Discourse2` = 'Null_N-L1*Maintain')
saveRDS(df_model_3, "./rds/df_model_3.rds")
#df_narration$ref_type2 <- factor(df_narration$ref_type2,levels = c("NOM", "PRO", "CL", "NULL"))
```

>>>>

# statistics libraries
library(brms) # bayesian modeling
library(bayesplot) # plot options for bayesian models
bayesplot_theme_set(new = theme_bw()) # set plot theme
library(tidybayes)
library(bayestestR)

# theme function for ggplot2
theme_apa <- function(base_size = 10, base_family = "serif", box = FALSE) {
  adapted_theme <- ggplot2::theme_bw(base_size, base_family) +
    ggplot2::theme(legend.position = "bottom",
                   plot.title = ggplot2::element_text(size = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, ggplot2::rel(14), 0))
                   # , axis.title = ggplot2::element_text(size = ggplot2::rel(1.1))
                   , axis.title.x = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(ggplot2::rel(12), 0, 0, 0))
                   , axis.title.y = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, ggplot2::rel(12), 0, 0))
                   , axis.title.y.right = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(12)))
                   , axis.ticks.length = ggplot2::unit(ggplot2::rel(6), "points")
                   , axis.text = ggplot2::element_text(size = ggplot2::rel(0.9))
                   , axis.text.x = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(ggplot2::rel(6), 0, 0, 0))
                   , axis.text.y = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(0, ggplot2::rel(6), 0, 0))
                   , axis.text.y.right = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(6)))
                   , axis.line = ggplot2::element_line()
                   # , axis.line.x = ggplot2::element_line()
                   # , axis.line.y = ggplot2::element_line()
                   , legend.title = ggplot2::element_text()
                   , legend.key = ggplot2::element_rect(fill = NA, color = NA)
                   , legend.key.width = ggplot2::unit(ggplot2::rel(20), "points")
                   , legend.key.height = ggplot2::unit(ggplot2::rel(20), "points")
                   , legend.margin = ggplot2::margin(
                     t = ggplot2::rel(16)
                     , r = ggplot2::rel(16)
                     , b = ggplot2::rel(16)
                     , l = ggplot2::rel(16)
                     , unit = "points"
                   )
                   , panel.spacing = ggplot2::unit(ggplot2::rel(14), "points")
                   , panel.grid.major.x = ggplot2::element_blank()
                   , panel.grid.minor.x = ggplot2::element_blank()
                   , panel.grid.major.y = ggplot2::element_blank()
                   , panel.grid.minor.y = ggplot2::element_blank()
                   , strip.background = ggplot2::element_rect(fill = NA, color = NA)
                   , strip.text.x = ggplot2::element_text(size = ggplot2::rel(1.2), margin = ggplot2::margin(0, 0, ggplot2::rel(10), 0))
                   , strip.text.y = ggplot2::element_text(size = ggplot2::rel(1.2), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(10)))
    )
  if(box) {
    adapted_theme <- adapted_theme + ggplot2::theme(panel.border = ggplot2::element_rect(color = "black"))
  } else {
    adapted_theme <- adapted_theme + ggplot2::theme(panel.border = ggplot2::element_blank())
  }
  adapted_theme
}

@@

# remove subject 13, native but home language is home sign instead of TiD
df_narration %<>% subset(Subject != 13)

@@

# Posterior plot for reference type
df_model_1 <- mcmc_intervals_data(model_1, pars = vars(starts_with("b_")))
df_model_1$parameter %<>% dplyr::recode(`b_muNominal_Intercept` = "Nom_Intercept",
                                        `b_muNull_Intercept` = "Null_Intercept",
                                        `b_muNominal_Nativeness1` = "Nom_DoD",
                                        `b_muNull_Nativeness1` = "Null_DoD",
                                        `b_muNominal_Discourse1` = "Nom_Intro",
                                        `b_muNominal_Discourse2` = "Nom_Maintain",
                                        'b_muNominal_Nativeness1:Discourse1' = 'Nom_DoD*Intro',
                                        'b_muNominal_Nativeness1:Discourse2' = 'Nom_DoD*Maintain',
                                        'b_muNull_Nativeness1:Discourse1' = 'Null_DoD*Intro',
                                        'b_muNull_Nativeness1:Discourse2' = 'Null_DoD*Maintain',
                                        `b_muNull_Discourse1` = "Null_Intro",
                                        `b_muNull_Discourse2` = "Null_Maintain")
saveRDS(df_model_1, "./rds/df_model_1.rds")

@@

# Posterior plot for reference type
df_model_3 <- mcmc_intervals_data(model_3, pars = vars(starts_with("b_")))
df_model_3$parameter %<>% dplyr::recode(`b_muNominal_Intercept` = "Nom_Intercept",
                                        `b_muNull_Intercept` = "Null_Intercept",
                                        `b_muNominal_Group2M1` = "Nom_Late1-Late2",
                                        `b_muNominal_Group3M2` = "Nom_Early-Late1",
                                        `b_muNominal_Discourse1` = "Nom_Intro",
                                        `b_muNominal_Discourse2` = "Nom_Maintain",
                                        `b_muNominal_Group2M1:Discourse1` = 'Nom_L1-L2*Intro',
                                        `b_muNominal_Group3M2:Discourse1` = 'Nom_E-L1*Intro',
                                        `b_muNominal_Group2M1:Discourse2` = 'Nom_L1-L2*Maintain',
                                        `b_muNominal_Group3M2:Discourse2` = 'Nom_E-L1*Maintain',
                                        `b_muNull_Group2M1` = "Null_Late1-Late2",
                                        `b_muNull_Group3M2` = "Null_Early-Late1",
                                        `b_muNull_Discourse1` = "Null_Intro",
                                        `b_muNull_Discourse2` = "Null_Maintain",
                                        `b_muNull_Group2M1:Discourse1` = 'Null_L1-L2*Intro',
                                        `b_muNull_Group3M2:Discourse1` = 'Null_E-L1*Intro',
                                        `b_muNull_Group2M1:Discourse2` = 'Null_L1-L2*Maintain',
                                        `b_muNull_Group3M2:Discourse2` = 'Null_E-L1*Maintain')
saveRDS(df_model_3, "./rds/df_model_3.rds")

#df_narration$ref_type2 <- factor(df_narration$ref_type2,levels = c("NOM", "PRO", "CL", "NULL"))
```
